### 2019-02-11 1-Preamble/4-Acknowledgement/acknowledgement.tex
Version 0.1
Started to copy/paste my latest paper

@@

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année.
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.

>>>>

% TODO financial thanks

This work is supported by
the French National Research Agency (ANR), under the projects BADASS, SOGREEN and EPHYL (grants \emph{XXX}, \emph{N ANR-14-CE28-0025-02} and \emph{N ANR-16-CE25-0002-03}),
by R\'egion Bretagne, France,
the French Ministry of Higher Education and Research (MENESR),
by \'Ecole Normale Sup\'erieure de Paris-Saclay.
by European Union, through the European Regional Development Fund (ERDF),
and by Ministry of Higher Education and Research, Brittany and Rennes Métropole, through the CPER Project \emph{SOPHIE / STIC \& Ondes}.

@@

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année. Je t'aime chaton, impressionnant !
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.
Yo te quiero gatita, ¡impresivo!

### 2019-02-11 2-Chapters/1-Chapter/chapter1.tex
Started to copy/paste my latest paper

\item
    \emph{Multi-Player Bandits Revisited}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \texttt{www.cs.cornell.edu/conferences/alt2018}), Lanzarote, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01629733}.

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access}},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2018.ieee-wcnc.org}), Barcelone, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01705292}.

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings}},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \texttt{crowncom.org/2017}), Lisboa, Portugal, Septembre $2017$,
    \texttt{hal.inria.fr/hal-01575419},
    \textbf{Best Paper Award}.

@@

% =============================================================================
\subection{Submitted works or in progress works waiting for a new submission}

\begin{itemize}
\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \texttt{hal.inria.fr/hal-02006471}.

@@

\paragraph{Responsabilities}
    president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \texttt{bitbucket.org/scee_ietr/phd-student-day-ietr-2017-bonnefoi-and-besson/downloads/poster.pdf}}.
    I also helped for the organization and presented another poster\footnote{Cf. \texttt{bitbucket.org/lbesson/phd-student-day-ietr-2018/downloads/poster.pdf}} at IETR seminar (\texttt{seminar-ietr-18.sciencesconf.org}), held in Vannes in June $2018$.

    \paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \texttt{ewrl.wordpress.com/ewrl14-2018}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \uref{https://nips.cc/Conferences/2018/}{\emph{NeurIPS}} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

>>>>

\item
    \emph{Multi-Player Bandits Revisited},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \texttt{www.cs.cornell.edu/conferences/alt2018}), Lanzarote, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01629733}.

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2018.ieee-wcnc.org}), Barcelone, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01705292}.

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \texttt{crowncom.org/2017}), Lisboa, Portugal, Septembre $2017$,
    \texttt{hal.inria.fr/hal-01575419},
    \textbf{Best Paper Award}.

@@

% =============================================================================
\subsection{Submitted works or in progress works waiting for a new submission}

\begin{itemize}
\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \texttt{hal.inria.fr/hal-02006471}.

@@

\paragraph{Responsabilities}
    president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \texttt{hal.inria.fr/hal-02013839/document}}.
    I also helped for the organization and presented another poster\footnote{Cf. \texttt{hal.inria.fr/hal-02013847/document}} at IETR seminar (\texttt{seminar-ietr-18.sciencesconf.org}), held in Vannes in June $2018$.

    \paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \texttt{ewrl.wordpress.com/ewrl14-2018}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \href{https://nips.cc/Conferences/2018/}{\emph{NeurIPS}} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

### 2019-02-11 2-Chapters/4-Chapter/chapter4.tex
Better outline
Started to copy/paste my latest paper

- ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \verb{https://perso.crans.org/besson/articles/BMBM__IEEE_WCNC_2019.pdf}

@@

@@

@@

- ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \verb{https://perso.crans.org/besson/articles/BMBM__IEEE_WCNC_2019.pdf}

@@

>>>>

- ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \texttt{https://perso.crans.org/besson/articles/BMBM\_\_IEEE\_WCNC\_2019.pdf}

@@

\input{2-Chapters/4-Chapter/CROWNCOM2017.tex}

@@

\input{2-Chapters/4-Chapter/ICT2018_and_WCNC2019.tex}

@@

% - ``Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions'', see \texttt{https://perso.crans.org/besson/articles/BMBM\_\_IEEE\_WCNC\_2019.pdf}

\input{2-Chapters/4-Chapter/WCNC2019_restransmissions.tex}

@@

% ----------------------------------------------------------------------------
\section{Appendix for Chapter 4}
\label{sec:4:appendix}
